---
title: "2022-06-06  to  2022-06-12  ( Fitbit Visualizations )"
date: "2022-06-06"
---

```{r setup, echo = FALSE}

knitr::opts_chunk$set(fig.width = 12,
                      fig.height = 10, 
                      fig.align = "center",
                      warning = FALSE, 
                      message = FALSE,
                      comment = FALSE,
                      echo = FALSE, 
                      eval = TRUE,
                      cache = FALSE)

date_start = "2022-06-06"
date_end = "2022-06-12"
verbose = as.logical(FALSE)

CRS_value = as.integer(4326)
asc_desc_linestring = as.character("")

```

<br>

### [**heart rate time series**](#anchor_heart_rate_ts)
<a id="anchor_heart_rate_ts"></a>

```{r, out.height = '1100px'}

#.......................
# heart rate time series
#.......................

heart_dat = readRDS(file = "heart_dat_2022-06-06.RDS")
heart_dat$plt

```

```{r}

#...............................................
# DT::datatable() as option to download the data  [ heart rate time series ]
#...............................................

dt_heart_rate_data = data.table::rbindlist(heart_dat$heart_rate_intraday)

dt_heart_rate = DT::datatable(data = dt_heart_rate_data,
                              rownames = FALSE,
                              extensions = 'Buttons',
                              options = list(pageLength = 10,
                                             dom = 'Bfrtip',
                                             buttons = list(list(extend = 'csv',
                                                                 filename = 'heart_rate_time_series'))))
dt_heart_rate

```

<br>

### [**heart rate heatmap**](#anchor_heart_heatmap)
<a id="anchor_heart_heatmap"></a>

```{r, out.height = '1100px'}

#............................
# heart rate intraday heatmap [ plot options: https://yihui.org/knitr/options/#plots ]
#............................

heart_intra = heart_dat$heart_rate_intraday

hrt_heat = fitbitViz::heart_rate_heatmap(heart_rate_intraday_data = heart_intra, 
                                         angle_x_axis = 0)
hrt_heat

```

<br>

### [**heart rate variability during sleep time**](#anchor_heart_variability)
<a id="anchor_heart_variability"></a>

```{r}

#.......................
# heart rate variability
#.......................

hrt_rt_var = fitbitViz::heart_rate_variability_sleep_time(heart_rate_data = heart_dat,
                                                          sleep_begin = "00H 40M 0S",
                                                          sleep_end = "08H 00M 0S",
                                                          ggplot_hr_var = TRUE,
                                                          angle_x_axis = 25)
hrt_rt_var$hr_var_plot

```

```{r}

#..............................................
# DT::datatable() of the heart rate variability
#..............................................

dt_heart_rate_var = DT::datatable(data = hrt_rt_var$hr_var_data,
                                  rownames = FALSE,
                                  extensions = 'Buttons',
                                  options = list(pageLength = 10,
                                                 dom = 'Bfrtip',
                                                 buttons = list(list(extend = 'csv',
                                                                     filename = 'heart_rate_variability'))))

dt_heart_rate_var

```

<br>

### [**sleep time series**](#anchor_sleep_ts)
<a id="anchor_sleep_ts"></a>

```{r, out.height = '1100px'}

#.......................
# sleep data time series
#.......................

sleep_ts = readRDS(file = "sleep_ts_2022-06-06.RDS")

sleep_ts$plt_lev_segments

```

```{r}

#.....................................
# DT::datatable() of the sleep heatmap
#.....................................

dt_sleep_heatmap = DT::datatable(data = sleep_ts$heatmap_data,
                                 rownames = FALSE,
                                 extensions = 'Buttons',
                                 options = list(pageLength = 10,
                                                dom = 'Bfrtip',
                                                buttons = list(list(extend = 'csv',
                                                                    filename = 'sleep_heat_map'))))

dt_sleep_heatmap

```

<br>

### [**GPS data of outdoor activities**](#anchor_gps_outdoor)
<a id="anchor_gps_outdoor"></a>

```{r}

#...................
# extract the log-id   (required for the GPS data)
#...................

log_id = readRDS(file = "log_id_2022-06-06.RDS")

flag_no_gps_data = FALSE

msg = ''

if (is.null(log_id)) {
  
  flag_no_gps_data = TRUE
  
  msg = glue::glue("For the time interval from '{date_start}' to '{date_end}' the 'log-id' does not exist! Therefore both the 'Leaflet' and the '3-dimensional Rayshader Map' won't be visualized!")
}

```

```{r}

#....................................................
# return the gps-ctx data.table for the output log-id
#....................................................

if (!flag_no_gps_data) {

  res_tcx = readRDS(file = "res_tcx_2022-06-06.RDS")
  
  if (is.null(res_tcx)) {
    
    flag_no_gps_data = TRUE

    msg = glue::glue("For the time interval from '{date_start}' to '{date_end}' and log-id: '{log_id}', there are no GPS data available! Both the 'Leaflet' and the '3-dimensional Rayshader Map' won't be visualized!")
  }
}

```

`r sprintf("<span style='color: %s;'>%s</span>", 'red', msg)`

<br>

### [**Leaflet Map of Point Coordinates**](#anchor_leaflet_coords)
<a id="anchor_leaflet_coords"></a>


```{r}

#................................
# Create the Leaflet / LeafGL Map
#................................


if (!flag_no_gps_data) {
  
  res_lft = fitbitViz::leafGL_point_coords(dat_gps_tcx = res_tcx,
                                         color_points_column = 'AltitudeMeters',
                                         provider = leaflet::providers$Esri.WorldImagery,
                                         option_viewer = rstudioapi::viewer,
                                         CRS = CRS_value)
  res_lft
}

```

<br>

```{r}

#.................................
# DT::datatable() for the GPS data
#.................................

if (!flag_no_gps_data) {

  dt_gps_tcx = DT::datatable(data = res_tcx,
                             rownames = FALSE,
                             extensions = 'Buttons',
                             class = 'white-space: nowrap',                 # unwrap the column-contents so that rows become flat, see:  https://github.com/rstudio/DT/issues/353
                             options = list(pageLength = 10,
                                            dom = 'Bfrtip',
                                            buttons = list(list(extend = 'csv',
                                                                filename = 'GPS_TCX_data'))))
  
  dt_gps_tcx
}

```

<br>

### [**3-dimensional Rayshader Map of the Activities**](#anchor_3d_rayshader)
<a id="anchor_3d_rayshader"></a>

```{r}

#...................................................
# compute the sf-object buffer and the raster-extend  (1000 meters buffer)
#...................................................

if (!flag_no_gps_data) {

  sf_rst_ext = readRDS(file = "sf_rst_ext_2022-06-06.RDS")
}

```

```{r}

#..................................................................
# Download the Copernicus DEM 30m elevation data
# there is also the option to download the DEM 90m elevation data
# which is of lower resolution but the image size is smaller which
# means faster download
#
# In case that I don't have a raster then set the 'flag_no_gps_data'
# parameter to TRUE (it is required for the rayshader map)
#..................................................................

if (!flag_no_gps_data) {
  
  if (file.exists("INIT_INVALID_PATH.tif")) {
    
    raysh_rst = raster::raster("INIT_INVALID_PATH.tif")
  }
  else {
    
    flag_no_gps_data = TRUE
  }
}

```

```{r}

#............................................................................................................................
# If the GPS route is an *ascending & descending* route we can convert the GPS (TCX) data to a spatial *LINESTRING* by
# using the maximum altitude as a *split point* of the route to visualize the ascending route in *blue* and the descending in 
# *red* (there is also the alternative to specify the split point based on time using the **time_split_asc_desc** parameter)
#............................................................................................................................

if (!flag_no_gps_data) {

  #................................................................................................    by default create a linestring
  linestring_dat = sf::st_as_sf(x = res_tcx, coords = c("longitude", "latitude"), crs = CRS_value)
  linestring_dat = sf::st_combine(x = linestring_dat)
  linestring_dat = sf::st_cast(x = linestring_dat, "LINESTRING")
  #................................................................................................ 
  
  if (asc_desc_linestring != "") {                              # in case that the 'asc_desc_linestring' parameter is not an empty string I expect it to be either a boolean or a lubridate::hms('17:05:00') object
    
    if (asc_desc_linestring %in% c('TRUE', 'FALSE')) {
    
      if (as.logical(asc_desc_linestring)) {                    # must be TRUE
        
        linestring_dat = fitbitViz::gps_lat_lon_to_LINESTRING(dat_gps_tcx = res_tcx,
                                                              CRS = CRS_value,
                                                              time_split_asc_desc = NULL,    # if NULL defaults to ascending max. value of GPS for peak then descending
                                                              verbose = verbose)
      }
    }
    else {
      
      conv_lubr = lubridate::hms(asc_desc_linestring)                                         # convert the input character string to lubridate object and verify that it is a lubridate objec to class 'Period'
      
      if (all(names(attributes(conv_lubr)) %in% c("year", "month", "day", "hour", "minute", "class"))) {
        
        linestring_dat = fitbitViz::gps_lat_lon_to_LINESTRING(dat_gps_tcx = res_tcx,
                                                            CRS = CRS_value,
                                                            time_split_asc_desc = conv_lubr,
                                                            verbose = verbose)
      }
    }
  }
}

```

```{r}

#...............................................................................................
# then we create the *'elevation_sample_points' data.table parameter* for the *3-dim* plot
# based on the *min.*, *middle*  and *max.* altitude of the previously computed *'res_tcx'* data
#...............................................................................................

if (!flag_no_gps_data) {

  idx_3m = c(which.min(res_tcx$AltitudeMeters), 
             as.integer(length(res_tcx$AltitudeMeters) / 2), 
             which.max(res_tcx$AltitudeMeters))
  
  cols_3m = c('latitude', 'longitude', 'AltitudeMeters')
  dat_3m = res_tcx[idx_3m, ..cols_3m]

}

```

```{r}

#.......................................................
# finally we visualize the *3-dimensional Rayshader Map*
#.......................................................

if (!flag_no_gps_data) {

  snapshot_rayshader_path = tempfile(fileext = '.png')

  rgl::open3d(useNULL = TRUE)                       # this removes the second rgl-popup-window

  fitbitViz::rayshader_3d_DEM(rst_buf = raysh_rst,
                              rst_ext = sf_rst_ext$raster_obj_extent,
                              linestring_ASC_DESC = linestring_dat,
                              elevation_sample_points = dat_3m,
                              zoom = 0.3,
                              windowsize = c(1000, 800),
                              add_shadow_rescale_original = FALSE,
                              verbose = verbose)

  rgl::rgl.snapshot(snapshot_rayshader_path)
  rgl::par3d(mouseMode = "trackball")   # options: c("trackball", "polar", "zoom", "selecting")
  rgl::rglwidget()
}

```

<br>
